Update Meeting: 23-09-2021

### 2021-09-24 analysis/update_meeting_23_09_2021.Rmd
select the right columns for DT

```{r YiYp_adj, include = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE)}
yiyp_adj.DT <- proxyMR_MR_paths_summary_yiyp_adj %>% dplyr::select(exposure_description, outcome_description, exposure_sex, starts_with("yiyp_IVW"))

DT::datatable(yiyp_adj.DT, width = "100%") %>% formatRound(columns=c('YiXi_IV_exact_overlap', 'YiXi_IV_sig_overlap'), digits = 3)

@@

>>>>

```{r YiYp_adj, include = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE)}
yiyp_adj.DT <- proxyMR_MR_paths_summary_yiyp_adj %>% dplyr::select(exposure_description, outcome_description, exposure_sex, yiyp_IVW_beta, yiyp_IVW_se, yiyp_IVW_pval, yiyp_IVW_beta_adj, yiyp_IVW_se_adj, yiyp_IVW_pval_adj)

format_round_cols <- colnames(dplyr::select_if(yiyp_adj.DT, is.numeric))
DT::datatable(yiyp_adj.DT, width = "100%") %>% formatRound(columns=format_round_cols, digits = 3)

@@

create_fig(fig_dat, custom_col)
